---
title: "MTM: Networks Session"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(MTM)
library(igraph)
knitr::opts_chunk$set(echo = FALSE)

# `?` <- function(e1, e2) {
#   h <- .Primitive("?")(e1, e2)
#   tools:::Rd2txt(utils:::.getHelpFile(as.character(h)))
# }
```

## Warmup

For this, you should generally run the code, examine the results, and then answer the questions individually or amongst a small group.

Some questions entail changing or filling in missing function arguments. These are marked with `\`???\`("Explanatory message.")` placeholders.

For some of those, we suggest relevant functions with "hint: ?FUNCTION", as in `?FUNCTION` will prompt you with the documentation of a function that may be useful

There are some items marked with ASIDE; do *not* bother with these until you have finished all the material in the exercise. They are intended as extensions.

Finally, this material is written using the `igraph` library. There are other libraries that provide the same basic functionality, but via different approaches, e.g. `networkx`

### Exercise A

The igraph library has several functions to create common network structures, including both deterministic ones (**e.g.** fully connected graphs) and probabilistic generators (**e.g.** Erdos-Renyi random graphs)

In `igraph`, the general convention is that the deterministic functions start with `make_...`, and the probabilistic generators start with `sample_...`. You can see a list of the options by `??igraph::make_` and `??igraph::sample_`.


```{r intro_networks, exercise=TRUE}
ig10 <- make_full_graph(n = 10)
ig30 <- make_full_graph(n = 30)
ig10layout <- layout_with_graphopt(ig10)
ig30layout <- layout_with_graphopt(ig30)
plot(ig10, layout = ig10layout); print(ig10)
plot(ig30, layout = ig30layout); print(ig30)

ig10gnp <- sample_gnp(10, 0.2)
ig30gnp <- sample_gnp(30, 0.2)
plot(ig10gnp, layout = ig10layout); print(ig10gnp)
plot(ig30gnp, layout = ig30layout); print(ig30gnp)
```

```{r intro_networks_A_quiz}
quiz(
  question("Describe the graphs these functions create.", answer("", correct = TRUE), type = "learnr_text")
)
```

### ASIDE

Note that by default, plotting an igraph object gives a different layout each time

```{r intro_networks_aside, exercise=TRUE}
plot(ig10); plot(ig10) # compare these two
#' To get the same plot, you can generate a layout for a graph (as above)
plot(ig10, layout = ig10layout); plot(ig10, layout = ig10layout) # compare these two 
#' this can be useful for comparing across graphs as well
plot(ig10, layout = ig10layout); plot(ig10gnp, layout = ig10layout)

```

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

